\begin{abstract}
Satellite communication has become firmly established as one of three basic techniques for long-distance telecommunications, alongside cables and terrestrial wireless networks. With more than 120 Indian satellites in orbit and many more in development by the Indian Space Research Organisation (ISRO), the domain of satellite engineering is a promising one. One of the most important aspects of satellite communication systems is the multiplexing of signals to send multiple streams of data simultaneously over a communications link. Multiplexing preserves channel resources and improves the temporal and computational complexity of the system. While conventional systems that implement multiplexing are still in use, these offer low data rates and high error rates. Thus, Filter Bank-based multiplexing solutions are gaining popularity in the domain of satellite systems, as they achieve high data rates and relatively low error rates. Trans-multiplexers are applications of filter banks that convert Time-division-multiplexed (TDM) signals to Frequency-division-multiplexed (FDM) signals for transmission over a channel. Most Trans-multiplexer systems use Fourier and Cosine Transforms for filter design and signal reconstruction, which do not offer Perfect Reconstruction (PR) as the time domain information of the signal is discarded. This paper presents an algorithm that utilizes Wavelet Transform techniques for filter design to be used in Trans-multiplexers in satellite systems. The work realizes the designed filters and Trans-multiplexer system in MATLAB, and its performance is evaluated by testing with various Channel Models and Mother Wavelets.

\end{abstract}

