\begin{thebibliography}{}
\bibitem{b1}
ISRO Research Proposals, 2021. \textit{ISRO Respond Basket.} [online] isro.gov.in., SAC-009 pg 44-45, Available at: https://www.isro.gov.in/sites/default/files/article-files/capacity-building/supported-areas-of-research/respond\_basket\_book-\_final-1.pdf, [Accessed 23 August 2021].

\bibitem{b2} 
Penedo, S.R.M., Netto, M.L. \& Justo, J.F. Designing digital filter banks using wavelets. \textit{EURASIP J. Adv. Signal Process. 2019}, 33 (2019). https://doi.org/10.1186/s13634-019-0632-6

\bibitem{b3}
Peter Yusuf Dibal, Elizabeth Onwuka, James Agajo, \& Caroline Alenoghena (2019). Analysis of Wavelet Transform Design via Filter Bank Technique. In \textit{Wavelet Transform and Complexity.} IntechOpen.

\bibitem{b4}
C. Sidney Burrus, \textit{Wavelets and Wavelet Transforms.} OpenStax CNX. Aug 6, 2018 http://cnx.org/contents/110bab92-1948-4958-b1c7-8fc0926c392c\@5.16. 

\bibitem{mallat_paper}
S. G. Mallat, ``A theory for multiresolution signal decomposition: the wavelet representation,'' in \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 11, no. 7, pp. 674-693, July 1989, doi: 10.1109/34.192463.

\bibitem{b5}
M. Vetterli and C. Herley, ``Wavelets and filter banks: theory and design,'' in \textit{IEEE Transactions on Signal Processing}, vol. 40, no. 9, pp. 2207-2232, Sept. 1992, doi: 10.1109/78.157221.

\bibitem{b6}
Cruz-Roldán, F., Bravo-Santos, Á., Martı́n-Martı́n, P. and Jiménez-Martı́nez, R., ``Design of multi-channel near-perfect-reconstruction transmultiplexers using cosine-modulated filter banks'', \textit{Elsevier Signal Processing} Volume 83 Issue, 5 May 2003, Pages 1079-1091

\bibitem{b7}
Ramachandran, R., \& Kabal, P. (1990). ``Transmultiplexers: Perfect reconstruction and compensation of channel distortion''. \textit{Signal Processing}, 21, 261-274.

\bibitem{b8}
Martin Vetterli (1986). ``Filter banks allowing perfect reconstruction''. \textit{Signal Processing}, 10(3), 219-244.

\bibitem{b9}
M. Vetterli, ``Perfect transmultiplexers,'' ICASSP '86. IEEE International Conference on Acoustics, Speech, and Signal Processing, 1986, pp. 2567-2570, doi: 10.1109/ICASSP.1986.1169290.

\bibitem{b10}
A. Vishwakarma, A. Kumar, \& G.K. Singh (2017). ``Design of near-perfect-reconstructed transmultiplexer using different modulation techniques: A comparative study''. Journal of King Saud University - Engineering Sciences, 29(3), 257-263.

\bibitem{b11}
Ali Naci Akansu, Richard A. Haddad, and Hakan Caglar ``Perfect reconstruction binomial QMF-wavelet transform'', Proc. SPIE 1360, \textit{Visual Communications and Image Processing '90:} Fifth in a Series, (1 September 1990); https://doi.org/10.1117/12.24246

\bibitem{b12}
Mon AT, Aye SM, Tun HM, Naing, and ZM Moe WK, ”Analysis of multichannel filter banks-based tree-structured design for communication systems”. \textit{Software Engineering}. 2018; 6(2) : pg 37-46

\bibitem{b13}
Ting Liu, \& Tongwen Chen (2000), ``Optimal design of multi-channel transmultiplexers''. \textit{Elsevier Journal on Signal Processing}, 80(10), 2141-2149.

\bibitem{b14}
M. Vetterli, ``A theory of multirate filter banks,'' in \textit{IEEE Transactions on Acoustics, Speech, and Signal Processing}, vol. 35, no. 3, pp. 356-372, March 1987, doi: 10.1109/TASSP.1987.1165137.

\bibitem{b15}
N. Mishra, P. Mishra, H. Shah and A. Banik, ``A design method using a set of objective functions for near-perfect reconstruction filter bank based transmultiplexer for onboard transparent processor,'' \textit{2013 International Conference on Signal Processing and Communication (ICSC)}, 2013, pp. 271-275, doi: 10.1109/ICSPCom.2013.6719796.

\bibitem{b16}
Akansu, A. N., Serdijn, W. A., \& Selesnick, I. W. (2010). Emerging applications of wavelets: A review. \textit{Physical Communication,} 3(1), 1-18. https://doi.org/10.1016/j.phycom.2009.07.001

\bibitem{mallat_book}
Mallat, Stéphane. (2009), ``A Wavelet Tour of Signal Processing,'' Third Edition \textit{Elsevier Academic Press}, 2009, ISBN 9780123743701

\bibitem{b17}
Mertins, A., \& Mertins, D. (1999), \textit{Signal Analysis: Wavelets, Filter Banks, Time-Frequency Transforms and Applications}, John Wiley \& Sons, Inc

\bibitem{b18}
Smith, J.O. ``Multirate Filter Banks'', in \textit{Spectral Audio Signal Processing}, http://ccrma.stanford.edu/~jos/sasp/Multirate\_Filter\_Banks.html, online book, 2011 edition, accessed 06-10-2021.

% \bibitem{b19}
% Ying-Jui Chen (2004). Wavelets and multirate filter banks : theory, structure, design, and applications, In \textit{MIT Research Libraries.}

\bibitem{b20}
MathWorks. 2021. Three-Channel Wavelet Transmultiplexer. [online] Available at: <https://in.mathworks.com/help/dsp/ug/three-channel-wavelet-transmultiplexer.html> [Accessed 6 October 2021].

\bibitem{dwt} A. Muhit, M. Islam, and M. Othman, ``Design Design and Analysis of Discrete Wavelet Transform (DWT) for Image Compression Using VHDL'', in \textit{ International Conference on Parallel and Distributed Processing Techniques and Applications (PDPTA), 2005}. Volume 1. CSREA Press 2005, pp. 157-160, Las Vegas, Nevada, USA, 2005, ISBN 1-932415-58-0. 

\bibitem{speech} IEEE Subcommittee on Subjective Measurements, ``IEEE Recommended Practices for Speech Quality Measurements'', \textit{IEEE Transactions on Audio and Electroacoustics}. vol 17, 227-46, 1969

\bibitem{channel} Lu Lu, Daoxing Guo, Aijun Liu, \& Maoqiang Yang (2012), ``Analysis of Channel Model for GEO Satellite Mobile Communication System'', In Proceedings of the \textit{2012 National Conference on Information Technology and Computer Science} (pp. 863-867). Atlantis Press.


\end{thebibliography}
