\chapter{Conclusion}
Multiplexing is an integral part of signal processing in satellite systems as it preserves channel resources while reducing the time and cost of signal transmission. The use of Filter bank-based multiplexers will help improve the performance and reliability of satellite communication systems. Trans-multiplexers are a widely explored application of Filter banks, which conventionally use Fourier-based filters to perform TDM-FDM conversion. This study proposes an algorithm to design Wavelet transform-based filters for Trans-multiplexer systems. The filters and the corresponding system are realized in MATLAB and are simulated under various conditions. The study evaluates the system using the Mean Squared Error (MSE) of the normalized signals. The work compares the performance of the Designed wavelet filters with other wavelet families as well as a similar Fourier-based conventional system. The Proposed system improves upon the MSE of the Conventional system by a factor of $10^{-2.5}$. The Time complexity of the Wavelet-based system is improved by a factor of $4.5$ which results in reduced signal processing time. The main limitation of the system is the poor reconstruction of signals with a high frequency of sharp fluctuations. Future studies can test the proposed algorithm by designing filters for different frequencies of operation. The Trans-multiplexer system proposed in this paper can be implemented on an FPGA/ASIC to test its performance in real-world conditions.

\chapter{Future Scope}
The application of Wavelet Transform in Filter Bank design is uncharted territory, leaving a lot of scope for future work. The use of the proposed filter design algorithm is not limited to the system proposed in this paper. The proposed algorithm can be applied to real-time systems in various frequency bands depending on the requirements of the application. Filter bank-based communication systems will be beneficial in satellite systems, which require low processing time and complexity while preserving system performance and reducing error rates. These systems are still in the process of being migrated to filter bank-based designs. The Trans-multiplexer system proposed in this paper can be implemented on an FPGA/ASIC to test its performance in real-world conditions. The filter coefficients can be fine-tuned to improve performance. Future studies can test the proposed algorithm by designing filters for different frequencies of operation.


