\chapter{Project road map}
\section{Literature Review}
This stage consists of in-depth review of the articles published in well known journals and conference proceedings.
\section{Simulation Stage}
\begin{itemize}
\item To setup a software based Power Electronics Test Bench for the virtual load emulation through public-domain circuit simulator, SEQUEL. The test bench consists of a virtual load model, IGBT based inverter and a current controller.
\item Different current control techniques for virtual load will be studied and tested on this software test bench. Their comparative merits and demerits and suitability for a real time emulation would be investigated through software simulation.
\item To write a load model and control algorithm for real-time implementation on a DSP platform.
\item Study the issues relating to the interfacing impedance.
\item Study the issues and simulation of non-linear active loads.
\item The results of current control techniques by computer simulation will presented in the second stage progress seminar.
\end{itemize}
\section{Hardware setup and Testing Stage}
\begin{itemize}
\item To simulate Virtual machine
\item To prepare a hardware setup and verify experimental results with the simulation results. 
\item To prepare hardware setup for bidirectional power flow.
\end{itemize}
\section{The final stage}
\begin{itemize}
\item To implement the modifications, corrections and suggestions obtained during previous presentations.
\item Preparation of a pre-synopsis report and its presentation
\item To prepare the final report and send it for review
\item To do the necessary corrections from the review report.
\item Final Presentation.
\end{itemize}
